### 2021-06-04 paper/report.tex
Add more precise draft for figures.

The model includes several other features, which are crucial to describe the evolution of the pandemic in 2020-2021. New virus strains with different profiles regarding infectiousness and disease progress can be introduced. Vaccinations induce immunity; vaccinated agents do not transmit the virus.\footnote{All of these approximations could be easily relaxed at the cost of a higher computational burden.} While vaccines are rolled out, priority may depend on age and occupation. Agents may demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First, polymerase chain reaction (PCR) tests directly reveal whether an individual is infected or not. PCR tests require some time to be processed and there are always aggregate capacity constraints. Second, rapid antigen tests yield immediate results. Specificity and sensitivity of these tests is set according to the XXX data.\comment[id=HM]{subsequent PCR tests, quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices, testing requirements before work, attending school, or visiting restaurants and shops.

@@

@@

\paragraph{Story by Figures}
\begin{itemize}
    \item Fig 2: Model fit and measures

          Aggregate. Refer to appendix for fits by age group and geographical region.

    \item Fig 3: Scenarios, Shapley. Why testing so effective. Form of TTI.

    \item Fig 4: Schooling scenarios? Including vacation effects in fall? Similar for Easter?

\end{itemize}

\paragraph{Points to mention}
\begin{itemize}
    \item Social structure / conditional block testing in families important (?)
    \item Trump-effect: More testing = more cases true for how long?
\end{itemize}

>>>>

The model includes several other features, which are crucial to describe the evolution of the pandemic in 2020-2021. New virus strains with different profiles regarding infectiousness and disease progress can be introduced. With a probability calibrated to XXX\comment[id=HM]{Klara, please add citatiion}, vaccinated agents become immune and they do not transmit the virus. While vaccines are rolled out, priority may depend on age and occupation. Agents may demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First, polymerase chain reaction (PCR) tests directly reveal whether an individual is infected or not. PCR tests require some time to be processed and there are always aggregate capacity constraints. Second, rapid antigen tests yield immediate results. Specificity and sensitivity of these tests is set according to the XXX data.\comment[id=HM]{subsequent PCR tests, quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices, testing requirements before work, attending school, or visiting restaurants and shops.

Identification

@@

Simulated data have very similar structure to data that is used for regression analyses. Can use as further plausbility check.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        Stringency index + multipliers

        Contact reduction $\times$ hygiene multiplier for different types of contacts

        potentially $\times$ seasonality

        else put seasonality separately
        \begin{itemize}
            \item Work
            \item School
            \item Other
        \end{itemize}

        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        Number of PCR tests

        Fraction of pupils with antigen tests

        Fraction of workers with antigen tests

        Fraction of vaccinations (effective = lagged by two weeks or date of vaccination?)

        \vskip2ex

        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \vskip3ex

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/disease_progression.png}
        Share known cases (estimated)

        Share B.1.1.7

        \vskip2ex

        \caption{Share of known cases and fraction of B.1.1.7 strain}
        \label{fig:share_known_cases_b117}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}

    \caption{Drivers of the pandemic and model fit, September 2020 to May 2021}
    \label{fig:pandemic_drivers_model_fit}

    Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

\end{figure}

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}
    \vskip3ex

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/disease_progression.png}

        Shapley values

        \vskip2ex

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}}
        \label{fig:decompisition total cases}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}

        Effects of social structure (implicit tracing) / effects of different types of testing

        \vskip2ex

        \caption{{\small Effects of different types of testing}}
        \label{fig:decomposition_tests}
    \end{subfigure}

    \caption{The effect of different interventions on recorded and actual infections}
    \label{fig:interventions_broad}

    Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

\end{figure}

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}
    \vskip3ex

    \caption{Schooling / maybe home office}
    \label{fig:interventions_school}

    Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

\end{figure}

\paragraph{Points to mention}
\begin{itemize}
    \item If anything too optimistic regarding vaccinations
    \item Social structure / conditional block testing in families important (?)
    \item Trump-effect: More testing = more cases true for how long?
\end{itemize}
